\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
 
\title{Tutorials}
\author{Group 41}
\begin{document}

\maketitle

\section{Tutorial 1}

On paper

\section{Tutorial 2}

\begin{enumerate}
    \item Structure? Application, up to us. Start off with theory.  Types of distribution, GEV, parameters, estimation with example. Perhaps Bayesian Style.
    \item Do we do joint, multivariate case? If there is time. Thoroughly understand what we are doing.
    \item Probability Weighted Moments? Go into it.
    \item Should Q-Q plots be covered mostly through the examples? Yes, do model testing in GUMBLE and GEV.
    \item In terms of proofs, how closely can we follow books? Pretty close while correctly referencing the books.
    \item Use Kolmogorov-Smirnov Tests.
    \item Methods of Parameter Estimation? Probability weighted moments, MATLAB methods (gevfit and evfit). Mention how it is tricky to implement in non-closed form.
    \item Should we include minima too? Could do if there is time, perhaps mention it.
    \item General Advice: Consistent Notation, Signpost everything (flow of the report) and correct referencing.
\end{enumerate}

\section{Tutorial 3}

\begin{enumerate}
    \item Bootstrapping Technique (Resample from original sample with replacement)
    \item Kolmogorov-Smirnov with estimated parameters.
    \item Cover page with contents.
    \item References, Harvard style.
    \item MLE - Implicit equation, iterate using iterative methods (Newton-Raphson Method)
\end{enumerate}

\section{Tutorial 4}

\begin{enumerate}
    \item Consistent Estimator. This is a basic property/requirement for estimators.
    \item Gather local data of earthquakes (We now have Taiwan/Philippines)
    \item Bayesian Analysis of things.
\end{enumerate}

\end{document}

